\documentclass{cheatsheet}

\begin{document}

\section{Checks}

\begin{multicols}{3}
\begin{emphbox}
  \begin{center}
    \dice{2d + dm + luck}

    Luck must be declared before rolling.

    \textbf{Boon / Bane:} best / worst two of \dice{3d}.
  \end{center}
\end{emphbox}

\begin{tabularx}{\linewidth}{Xl} \toprule
Difficulty & Target \\ \midrule
Simple & 2+ \\
Easy & 4+ \\
Routine & 6+ \\
Average & 8+ \\
Difficult & 10+ \\
Very Difficult & 12+ \\
Formidable & 14+ \\
Impossible & 16+ \\ \bottomrule
\end{tabularx}

\textbf{Doing multiple tasks:} increase difficulty one step.

\columnbreak

\begin{tabularx}{\linewidth}{lXr} \toprule
Effect & Result & Chain \textsc{dm} \\ \midrule
-6 or less & Exceptional Failure & -3 \\
-5 to -2 & Average Failure & -2 \\
-1 & Marginal Fail & -1 \\
0 & Marginal Success & 0 \\
1 to 5 & Average Success & 1 \\
6 or more & Exceptional Success & 2 \\ \bottomrule
\end{tabularx}

\subsection{Time}

\textbf{\dice{1d} seconds}\\
\textit{e.g.} shooting, punching, jumping

\textbf{\dice{1d} combat rounds}\\
\textit{e.g.} hurrying jump calculations

\textbf{\dice{1d $\times$ 10} seconds}\\
\textit{e.g.} rerouting power, opening a comms channel

\textbf{\dice{1d} minutes}\\
\textit{e.g.} first aid, basic technical tasks

\textbf{\dice{1d $\times$ 10} minutes}\\
\textit{e.g.} complex technical tasks, searching thoroughly

\textbf{\dice{1d} hours}\\
\textit{e.g.} building a shelter, moving through wilderness

\textbf{\dice{1d $\times$ 4} hours}\\
\textit{e.g.} researching a problem

\textbf{\dice{1d $\times$ 10} hours}\\
\textit{e.g.} repairing a damaged ship

\textbf{\dice{1d} days}\\
\textit{e.g.} combing a city for a missing person

\textbf{Going faster or slower by one step:} \diemod{$\pm 2$}.
\end{multicols}

\section{Combat}

\begin{multicols}{3}
\begin{emphbox}
  \begin{center}
    \dice{2d + dex {\normalfont or} int dm + Tactics Effect + Surprise}
  \end{center}

  \textbf{Tactics:} One combatant per side may make a check, adding
  the Effect to Initiative.

  \textbf{Surprise:} $\pm$ 6 (first round only).

  \begin{center}
    \textbf{Round (6 seconds)}
  \end{center}

  One \textbf{Significant Action} or two \textbf{Minor Actions}\\
  One \textbf{Minor Action}\\
  Any number of \textbf{Free Actions}\\
  Any number of \textbf{Reactions}
\end{emphbox}

\subsection{Significant Actions}

\textbf{Melee Attack}\\
\chrskillcheck{str {\normalfont or} dex}{Melee (specialism)}.

\textbf{Ranged Attack}\\
\chrskillcheck{dex}{Gun Combat (specialism)}.

\begin{tabularx}{\linewidth}{lX} \toprule
Bonus & \textsc{dm} \\ \midrule
Aiming & +1 per aim action (max +6) \\
Laser Sight & +1 if aiming \\
Short Range & +1 \\ \midrule
Penalty & \\ \midrule
Fast Moving & -1 per 10 relative m/round \\
Long Range & -2 \\
Extreme Range & -4 \\
Target Covered & -2 \\
Prone Target & -1 \\ \bottomrule
\end{tabularx}

\textbf{Short range:} up to $\times\frac{1}{4}$.\\
\textbf{Long range:} up to $\times 2$.\\
\textbf{Extreme range:} up to $\times 4$, or 100m if no scope.

\textbf{Miscellaneous}\\
Skill check, or full concentration, or is complicated.\\
\textit{e.g.} applying first aid, bypassing a security system.

\subsection{Minor Actions}

\textbf{Aim}\\
\diemod{+1} on the immediately following ranged attack.

\textbf{Change Stance}\\
Crouch or lie prone.

\textbf{Draw / Reload}\\
Draw, make ready for combat, or reload (unless noted otherwise in the
weapon description).

\textbf{Move}\\
Move a number of metres up to Movement score (usually 6 for humans).
Difficult terrain halves speed.  Being prone quarters speed.

\textbf{Miscellaneous}\\
Doesn't require concentration, or is simple.\\
\textit{e.g.} identifying equipment, picking something up.

\subsection{Reactions}

Each reaction gives \diemod{-1} on the next turn.

\textbf{Dodge}\\
Inflict the highest of the \textsc{dex} or Athletics (dex) \textsc{dm}
as a penalty to the Attack roll.

\textbf{Dive for Cover (vs Ranged)}\\
Inflict \diemod{-2} and reach cover within 1.5 metres.  If no cover,
only \diemod{-1}.  This skips the next turn.

\textbf{Parry}\\
In close combat, inflict Melee \textsc{dm} as a penalty to the Attack
roll.

\textbf{Opportunity Attack}\\
Attack if a combatant leaves close combat with \diemod{+2} to the
Attack roll.

\subsection{Extended Actions}

Roll for duration in rounds.  When taking damage, make a check with
the damage taken as a negative \textsc{dm} to see if that round's
progress counts.

Exceptional Failure means all progress is lost.

\subsection{Damage}

Add the Effect of the Attack roll to weapon damage (unless
Destructive, in which case no Effect but $\times 10$).  Melee attacks
also add \textsc{str} \textsc{dm}.

Armour reduces damage.  Effect 6 on the Attack roll deals at least 1
damage.

\begin{tabularx}{\linewidth}{Xr} \toprule
Cover & Bonus Armour \\ \midrule
Vegetation & +2 \\
Trees & +6 \\
Stone Wall & +8 \\
Vehicle & +10 \\
Armoured Vehicle & +15 \\
Fortifications & +20 \\ \bottomrule
\end{tabularx}

\subsection{Grappling}

Opposed \chrskillcheck{str {\normalfont or} dex}{Melee (unarmed)}.

\textbf{The winner may do one of the following:}\\
Force prone.\\
Disarm and (if Effect 6+) take the weapon.\\
Throw \dice{1d} metres for \dice{1d} damage.\\
Inflict 2 + Effect damage, ignoring armour.\\
Attack with a pistol, blade, or other small weapon.\\
Drag up to 3 metres.

\subsection{Dual Wielding}

\diemod{-2} to Attack rolls with both.

\subsection{Leadership}

One Traveller may make a Leadership check.  Their side gets Boon or
Bane dice equal to the Effect.

\subsection{Weapon Traits}

See page 75 of the core rulebook and page 7 of the Central Supply
Catalogue.
\end{multicols}

\begin{multicols}{2}
\section{Damage}

Damage is taken from \textsc{end}, then from \textsc{str} or
\textsc{dex}.  When two characteristics reach 0, the Traveller falls
unconscious.  When three characteristics reach 0:

\begin{tabularx}{\linewidth}{lX} \toprule
\dice{2d + dm} & Result \\ \midrule
2 or less & Destroyed gruesomely. \\
2 to 3 & Killed outright. \\
4 to 5 & Die without prompt medical attention.  Gain a disability. \\
6 to 7 & Die without prompt medical attention.  Lose \dice{1d} from one of max \textsc{str}, \textsc{dex}, \textsc{end}, and \dice{d3} from the others. \\
8 to 9 & Survive if given even basic medical attention.  Lose \dice{d3} from \textsc{str} and \textsc{end} without good medical care during recovery. \\
10 to 11 & Survive without assistance and make a full recovery with care. \\
12 or more & Survive and make a full recovery even without assistance. \\ \bottomrule
\end{tabularx}

\textbf{Final attack caused less than 3 points of damage:} \diemod{+4}.\\
\textbf{Final attack caused 4 to 6 points of damage:} \diemod{+2}.\\
\textbf{Final attack caused more than 6 points of damage:} \diemod{-2}.\\
Luck can be \textbf{permanently} spent to gain a bonus.

\vfill\columnbreak
\section{Healing}
\textbf{First Aid}\\
Recover \dice{Medic Effect}.  Must be done within one minute of
injury.

\textbf{Surgery}\\
Recover \dice{3 + Medic Effect}.  Requires a sick bay or hospital.

\textbf{Medical Care}\\
Recover \dice{3 + end dm + Medic Effect} check per day.  Requires a
sick bay or hospital and bed rest.  Cannot be done with three damaged
characteristics.

\textbf{Natural Healing}\\
Recover \dice{1d + end dm} (just \textsc{end dm} if in need of
surgery).  Requires bed rest.

\textbf{Augmentation and Medical Care}\\
If done in a lower-tier facility, checks take the difference between
the \textsc{tl} of the best highest augmentation and the facility as a
negative \textsc{dm}.

\textbf{Unconsciousness}\\
Make an \textsc{end} check to regain consciousness, with a cumulative
\diemod{+1}.
\end{multicols}
\end{document}
